Imputation Assessment

### 2023-07-24 minos/testing/imputation_testing.Rmd
Another version of the imputation step. This time, we "seed" variables where information is completely missing within a year (copy another wave onto and remove half of values). This is to give the imputater something to work with as complete missing within a year was causing big problems

---
title: "Imputation Assessment"
output: html_notebook
---

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

@@

  final.var <- final %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] > 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'final')

  complete.var <- complete %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] > 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'complete')

  imputed.var <- imputed %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] > 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'imputed')

  merged <- rbind(final.var, complete.var)
  merged <- rbind(merged, imputed.var)
  merged[[var]] <- as.factor(merged[[var]])

@@

>>>>

---
title: "Imputation Assessment"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  out.width = 3500
)
# 3000
# '100%'
rm(workingDir)
```

@@

  final.var <- final %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] >= 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'final')

  complete.var <- complete %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] >= 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'complete')

  imputed.var <- imputed %>% 
    dplyr::select(pidp, time, all_of(var)) %>%
    filter(.data[[var]] >= 0) %>%
    group_by(time, .data[[var]]) %>%
    count() %>%
    mutate(source = 'imputed')

  merged <- rbind(final.var, complete.var)
  merged <- rbind(merged, imputed.var)
  merged[[var]] <- as.factor(merged[[var]])
  merged$time = as.factor(merged$time)

@@

  p2 <- ggplot(data = merged, mapping = aes(x = time, y = n, group = .data[[var]], colour = .data[[var]])) +
    geom_line() +
    geom_point() +
    facet_grid(.~source) +
    theme(legend.position="none") +
    labs(title = var, subtitle = 'Counts by Level') +
    xlab('Year') +
    ylab('Count')

  print(p1)
  print(p2)

  var.norm <- merged %>%
    group_by(time, source) %>%
    mutate(total = sum(n)) %>%
    mutate(prct = (n / total))

  p3 <- ggplot(data = var.norm, mapping = aes(x = time, y = prct, fill=.data[[var]], position='dodge')) +
    geom_bar(stat = 'identity') +
    facet_grid(.~source) +
    theme(legend.position="none") +
    labs(title = var) +
    xlab('Year') +
    ylab('Proportion')
  print(p3)
}
